% #region config
\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{color}
\usepackage{hyperref}

\hypersetup{breaklinks=true,%
pagecolor=white,%
colorlinks=true,%
linkcolor=cyan,%
urlcolor=MyDarkBlue}

\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\jobTitle}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\links}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}


\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {\footnotesize #1} \hspace{2em}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\ 
  \indent {\small #2} \hfill {\footnotesize#3 (#4)}

}

\newenvironment{resume_work_bullets}{
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

% #endregion

\begin{document}

  \begin{resume_header}
    \name{Samuele Zanca}
    \jobTitle{Full-Stack Developer}
    \links{
      \href{mailto:samuele@zanca.dev}{samuele@zanca.dev}
      \hspace{1cm} +1 (201)706-7528
      \hspace{1cm}\href{http://github.com/metruzanca}{github.com/metruzanca}
      \hspace{1cm} \href{https://www.linkedin.com/in/samuelz/}{linkedin.com/in/samuelz}
    } 
  \end{resume_header}

  \begin{resume_section}{Work Experience}
    % DecHit
    \begin{resume_employer}{DecHit}{Full-Stack Developer \& Techlead}{}{11/2/20 - present}
      \begin{resume_work_bullets}
          \item Instructor for DecHit React Academy. Designed lesson projects to make the trainees learn by doing, then over iterations with code reviews and new features to implement I got them up to speed with Nodejs, React \& Redux.
          \item Lead a Team of 4 developers using the MERN stack to develop a microservice based application.
          \item Implemented CI/CD Pipelines using Gitlab, Jenkins, Docker and Kubernetes.
          \item Maintained and improved an Angular2+ application, reducing code complexity and duplication, resulting in faster development and easier integration with the Java Backend team.
          \item Maintained a Legacy React Cordova app while introducing greater testing and best practices to facilitate a transition to React Native for client Sisal SpA.
      \end{resume_work_bullets}
    \end{resume_employer}
    % Mia-Platform
    \begin{resume_employer}{Mia-Platform}{Full-Stack Developer}{}{07/8/20 - 10/16/20}
      \begin{resume_work_bullets}
          \item Worked on a cross-functional team, BURTON, to develop and deploy API, web dashboards and native mobile apps for a B2B client \href{https://www.foorban.com}{Foorban Srl}.
          \item Developed a microservice in Kotlin using the Ktor framework, Jackson and Retrofit2 following the BFF and Saga patterns.
          \item Developed two React dashboards using data from the previously mentioned kotlin API and Mia's custom CMS.
          \item Developed a PDF Microservice that allows the use of HTML as a familiar DSL for creating Shipping labels, receipts and custom size invoices.
          \item Prototyped a React app for live previewing of the PDFs using the \href{https://github.com/microsoft/monaco-editor}{Monaco-Editor}.
      \end{resume_work_bullets}
    \end{resume_employer}
    % TXT e-Solutions
    \begin{resume_employer}{TXT e-Solutions}{Software Engineer - Aerospace \& Defence}{}{09/15/19 - 07/8/20}
      \begin{resume_work_bullets}
          \item Acted as a point of reference/mentor for developers learning: Nodejs, React.js, Redux.js \& Typescript.
          \item Reduced all future bugs by 15\% by adopting Typescript and helping coworkers get up to speed.
          \item Lead the development of a React/Typescript web control panel for operating Flight Simulators via remotely via tablet for \href{https://www.leonardocompany.com/en/home}{Leonardo SpA}.
          \item Maintained c\# two Xamarin Mobile apps used by \href {https://www.itt.com/home}{ITT Inc} in Automotive industry for collecting diagnostic break data transfered over wifi and low power bluetooth.
          \item Developed a c\# app for collecting and processing flight data to reduce fuel costs in collaboration with \href{http://pace.txtgroup.com/products/flight-operations/pacelab-flight-profile-optimizer/}{IATA}.
          \item Developed a c\# WPF Simulator for training the proper use of the \href{https://www.elt-roma.com/product/adrian}{ADRIAN} system.
      \end{resume_work_bullets}
    \end{resume_employer}
    
  \end{resume_section}

  \begin{resume_section}{Personal Projects}
      \begin{resume_subsection}{Open Source: Nighttab Browser Extension [{\href{https://chrome.google.com/webstore/detail/nighttab/hdpcadigjkbcpnlcpbcohpafiaefanki}{chrome webstore}]}}
      \begin{subitems}
      \item Co-Maintainer of Nighttab, a productivity tool for bookmark management, currently serving {\raise.17ex\hbox{$\scriptstyle\sim$}}5K users.
      \end{subitems}
    \end{resume_subsection}
  \end{resume_section}

  \begin{resume_section}{Skills}
    JavaScript/Typescript,
    React,
    React
    Native,
    Redux,
    REST,
    HTML/CSS/SASS,
    Nodejs,
    Express/Fastify,
    C\#,
    Java,
    Kotlin,
    Ktor,
    gRPC,
    GraphQL,
    MySql,
    SQL,
    MongoDB,
    Firebase,
    Linux,
    Docker,
    Kubectl,
    Serverless,
    GCP
  \end{resume_section}

  \begin{resume_section}{Certifications}
    \begin{resume_subsection}[]{Cisco CCNA (networking)}
      \begin{subitems}
        \item Network fundamentals, network access, IP connectivity, IP services, security fundamentals, and automation.
      \end{subitems}
    \end{resume_subsection}
  \end{resume_section}

\end{document}